### 2020-06-22 README.Rmd
add zenodo badge to README

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/ropensci/taxadb.svg?branch=master)](https://travis-ci.org/ropensci/taxadb)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ropensci/taxadb?branch=master&svg=true)](https://ci.appveyor.com/project/cboettig/taxadb)
[![Coverage status](https://codecov.io/gh/ropensci/taxadb/branch/master/graph/badge.svg)](https://codecov.io/github/ropensci/taxadb?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/taxadb)](https://cran.r-project.org/package=taxadb)

>>>>

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/ropensci/taxadb.svg?branch=master)](https://travis-ci.org/ropensci/taxadb)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ropensci/taxadb?branch=master&svg=true)](https://ci.appveyor.com/project/cboettig/taxadb)
[![Coverage status](https://codecov.io/gh/ropensci/taxadb/branch/master/graph/badge.svg)](https://codecov.io/github/ropensci/taxadb?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/taxadb)](https://cran.r-project.org/package=taxadb)
[![peer-review](https://badges.ropensci.org/344_status.svg)](https://github.com/ropensci/software-review/issues/344)
[![DOI](https://zenodo.org/badge/130153207.svg)](https://zenodo.org/badge/latestdoi/130153207)
